\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-25 paper.qmd
Added title for Figure 17

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a and b, and two views of the fit in projections from $9\\text{-}D$, for the PBMC3k data ($n =  2622$ and $p = 9$). Layout a shows three-well separated clusters with big separation, while layout b shows close clusters. In $9\\text{-}D$, the data shows three clusters with two of them being close and one separated from the others. This is why b1, b2, and b3 shows a connected edge between the close clusters, as proven by @fig-pbmc-mse as a reasonable layout. Viewing the fitted model in $9\\text{-}D$, helps to see some unobserved patterns of the data: (i) dense points, and (ii) non-linear clusters. Videos of the langevitour animations for the models are available at <https://youtu.be/0cKX_HG_n0k> and <https://youtu.be/KhJvsRtaX04> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-height: 80%

@@

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 10
#| fig-width: 10
#| fig-cap: "Model in \\gD{}, on the layout a and three views of the fit in projections from $10\\text{-}D$, for the MNIST digit 1 data ($n =  7877$ and $p = 10$)."

>>>>

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a and b, and two views of the fit in projections from $9\\text{-}D$, for the PBMC3k data ($n =  2622$ and $p = 9$). Layout a shows three-well separated clusters with big separation, while layout b shows close clusters. In $9\\text{-}D$, the data shows three clusters with two of them being close and one separated from the others. This is why b1, b2, and b3 shows a connected edge between the close clusters, as proven by @fig-pbmc-mse as a reasonable layout. Viewing the fitted model in $9\\text{-}D$, helps to see some unobserved patterns of the data: (i) dense points, and (ii) non-linear clusters. Videos of the langevitour animations are available at <https://youtu.be/0cKX_HG_n0k> and <https://youtu.be/KhJvsRtaX04> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-height: 80%

@@

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 10
#| fig-width: 10
#| fig-cap: "Model in \\gD{}, on the layout a and three views of the fit in projections from $10\\text{-}D$, for the MNIST digit 1 data ($n =  7877$ and $p = 10$). There is a big non-linear cluster and a small clusterlocated very close to one corner of the big cluster. There is a twisted pattern that is hardly visible in the static plot. Video of the langevitour animation are available at <need to add the link>."

### 2024-09-25 paper.tex
Added title for Figure 17

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the layout
a and b, and two views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\(n =  2622\) and \(p = 9\)). Layout a shows
three-well separated clusters with big separation, while layout b shows
close clusters. In \(9\text{-}D\), the data shows three clusters with
two of them being close and one separated from the others. This is why
b1, b2, and b3 shows a connected edge between the close clusters, as
proven by Figure~\ref{fig-pbmc-mse} as a reasonable layout. Viewing the
fitted model in \(9\text{-}D\), helps to see some unobserved patterns of
the data: (i) dense points, and (ii) non-linear clusters. Videos of the
langevitour animations for the models are available at
\url{https://youtu.be/0cKX_HG_n0k} and
\url{https://youtu.be/KhJvsRtaX04} respectively.}

@@

\caption{\label{fig-mnist-tri-proj}Model in \gD{}, on the layout a and
three views of the fit in projections from \(10\text{-}D\), for the
MNIST digit 1 data (\(n =  7877\) and \(p = 10\)).}

>>>>

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the layout
a and b, and two views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\(n =  2622\) and \(p = 9\)). Layout a shows
three-well separated clusters with big separation, while layout b shows
close clusters. In \(9\text{-}D\), the data shows three clusters with
two of them being close and one separated from the others. This is why
b1, b2, and b3 shows a connected edge between the close clusters, as
proven by Figure~\ref{fig-pbmc-mse} as a reasonable layout. Viewing the
fitted model in \(9\text{-}D\), helps to see some unobserved patterns of
the data: (i) dense points, and (ii) non-linear clusters. Videos of the
langevitour animations are available at
\url{https://youtu.be/0cKX_HG_n0k} and
\url{https://youtu.be/KhJvsRtaX04} respectively.}

@@

\caption{\label{fig-mnist-tri-proj}Model in \gD{}, on the layout a and
three views of the fit in projections from \(10\text{-}D\), for the
MNIST digit 1 data (\(n =  7877\) and \(p = 10\)). There is a big
non-linear cluster and a small clusterlocated very close to one corner
of the big cluster. There is a twisted pattern that is hardly visible in
the static plot. Video of the langevitour animation are available at .}
